First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-07-20 paper/paper.tex
Formatting
Added a couple of TODOs in the Church encoding section

>>>>

\begin{todo}
  Explicitly mention how the constructs in this last part
  relate to their counterparts in the main part of the paper.
\end{todo}

\begin{todo}
  Figure out how recursive types fit into this framework. Church encodings can
  handle recursive types and so can our representation. This is also the case
  for Scott encodings, etc, and is the difference between Church and Scott
  encodings.

  Does our way of handling recursive types correspond to how any of
  those encodings handle recursive types?
\end{todo}
